R Notebook

### 2021-04-30 FEM_R/results.Rmd
Couple of small changes here and there, also started script to visualise by subgroup but its very much WIP

>>>>

```{r}
visCDComparison(c, bmi1, 'No Obesity', 'cancre')
visCDComparison(c, bmi1, 'No Obesity', 'diabe')
visCDComparison(c, bmi1, 'No Obesity', 'stroke')
visCDComparison(c, bmi1, 'No Obesity', 'hearte')
visCDComparison(c, bmi1, 'No Obesity', 'lunge')
visCDComparison(c, bmi1, 'No Obesity', 'employed')
visCDComparison(c, bmi1, 'No Obesity', 'retired')
visCDComparison(c, bmi1, 'No Obesity', 'anyadl')
visCDComparison(c, bmi1, 'No Obesity', 'anyiadl')
```
